Verifying Demonstrations

### 2018-08-14 paper/DB-anon-cred.tex

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but 
only \(l\) bits of the other.
The adversary now has two options.
First, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
them from the prover.
However, at this point the adversary must wait for the challenge bit 
\(b_{l+1}\) from the verifier and then relay that challenge to the prover to 
receive the correct \(r_i\) --- this relay will be detected.
The (better) alternative is to guess \(b\) and extract the \(|q|\) correct bits 
for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability \emph{per round} that the \ac{DBMF} 
adversary will guess it correctly.
Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
The adversary can also guess the remaining \(|q|-l\) bits, for which the 
probability of success is \(2^{-(|q|-l)}\) per round or, in total, 
\(2^{-(|q|-l)n}\).
Thus, the success probability of the \ac{DBMF} adversary is 
\(2^{-n}+2^{-(|q|-l)n}\).

@@

Finally, a malicious verifier who wants to impersonate a prover can guess the 
remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
the prover.
The probability that this succeeds is \(2^{-(|q|-l)}\) or, in total, 
\(2^{-(|q|-l)n}\).

>>>>

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but 
only \(l\) bits of the other.
The adversary now has two options.
First, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
them from the prover.
However, at this point the adversary must wait for the challenge bit 
\(b_{l+1}\) from the verifier and then relay that challenge to the prover to 
receive the correct \(r_i\) --- this relay will be detected.
The (better) alternative is to guess \(b\) and extract the \(|q|\) correct bits 
for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability \emph{per round} that the \ac{DBMF} 
adversary will guess it correctly.
Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
The adversary can also guess the remaining \(|q|-l\) bits, for which the 
probability of success is \(2^{-(|q|-l)}\) (note that this is independent of 
the rounds).
Thus, the success probability of the \ac{DBMF} adversary is \emph{at most} 
\(2^{-n}+2^{-(|q|-l)}\).

@@

Finally, a malicious verifier who wants to impersonate a prover can guess the 
remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
the prover.
The probability that this succeeds is, as above, \(2^{-(|q|-l)}\).

### 2018-08-14 paper/DistanceBounding.tex

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account. 
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate AND in his vicinity.
In this sense, \Ac{DB} protocols combines at the same time the classical properties of authentication protocols with the possibility of verifying the physical proximity.

The main attacks against \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
%Seb: the two following properties should be defined more precisely
  \item \Acf{DBDH}: similar to \ac{DBDF} but using the presence of an honest prover close to the verifier.
  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PKE} for discrete logarithms).

>>>>

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account. 
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate AND in his vicinity.
In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.

The main attacks against \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
%Seb: the two following properties should be defined more precisely
  \item \Acf{DBDH}: similar to \ac{DBDF} but using the presence of an honest prover close to the verifier.
  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation. \sonja{contrast with impersonating verifier}
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PKE} for discrete logarithms).

### 2018-08-14 paper/MANETs.tex
change to intro and system model

Since the cellular network can be shut down to keep protesters from
accessing the Internet, making phone calls or texting, we require a
different means of communications between protesters. This can be
accomplished by Bluetooth or WiFi, as demonstrated by
Briar~\cite{Briar} and FireChat~\cite{FireChat}, two examples of apps
for communication during protests via wireless mesh networking. An
alternative, although originally designed to work within 5G cellular
networks, is device-to-device communication (D2D)~\cite{D2D}. Specifically, the
outband and autonomous version D2D fits our scenario thanks to using
unlicensed spectrum and working without cellular coverage.

>>>>

Since the cellular network could be shut down to keep protesters from accessing the Internet, making phone calls or texting, we require a different means of communications between protesters. 
This could be accomplished by Bluetooth or WiFi communications, as demonstrated by Briar~\cite{Briar} and FireChat~\cite{FireChat}, two examples of applications for communication during protests via wireless mesh networking. 
An alternative, although originally designed to work within 5G cellular networks, is device-to-device communication (D2D)~\cite{D2D}. 
Specifically, the out-of-band and autonomous version D2D fits our scenario thanks to using unlicensed spectrum and working without cellular coverage.

### 2018-08-14 paper/RelatedWork.tex

An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}, is another recent development. 
This solution does not offer strong verifiability guarantees and thus has complemented by micro-counts made by humans to estimate his margin of error.

In general for all of the above methods, the more a crowd spreads out, the more difficult it will be to determine its size.
In particular, one of the challenge is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
These methods also have difficulty to capture the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).

One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting twice (violating eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Grace's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work with honest participants.

>>>>

An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}. 
This solution does not offer strong verifiability guarantees and thus is complemented by micro-counts made by humans to estimate their margin of error.

In general for all of the above methods, the more a crowd spreads out, the more difficult it is to determine its size.
In particular, one of the challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
These methods also have difficulties capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).

One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting more than once (violating eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Grace's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.

### 2018-08-14 paper/analysis-security.tex

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (proof shares) are indeed included.
As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, 
  \pi_{\wid}\)) are committed to the blockchain and available from public 
storage (see \cref{fig:ProtocolOverview}).
Alice and Bob can simply check that all of their proof shares are indeed there 
and thus the security of individual verifiability depends on the properties of 
the blockchain and storage.

\Cref{UniversalVerif} requires that also anyone can verify the result and that 
all participation proofs counted indeed are eligible.
As the proof shares are committed and stored publicly, anyone can download 
them, verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid}\)) the proofs and 
count them.
As for individual verifiability, the security of universal verifiability is 
reduced to the properties of the blockchain and storage but also the eligibility 
verification, which we will discuss next.

\subsection{Eligibility verifiability}%
\label{analysis-eligibility}

\Cref{EligibilityVerif} states that anyone must be able to determine the 
authenticity of the relevant attributes of the data.
We have several attributes that must be verifiable:
time of creation (temporal eligibility),
physical location of \(\sk_P\) at creation (spatial eligibility),
recognize two proofs from the same person (one-proof-per-person eligibility) and 
that the proof is indeed designated for the event (designated-event 
eligibility).
We will now analyse these.

\paragraph{Temporal eligibility}%
\label{analysis-temporal}

\Cref{TemporallyRelated} ensures freshness, \ie that Alice cannot simply 
resubmit an old proof as a new one.
In general, freshness requires the prover to respond to an unpredictable 
challenge.
The challenge here is to include the hash value at the head of the blockchain at 
the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof 
share).
As per construction of blockchains, the hash value at the head depends on the 
previous blocks in the chain.
Thus the predictability of \(t_s\) depends on the predictability of the blocks, 
which depends on the predictability of the transactions and the nonce needed by 
the miner.
The transactions in turn depend on the signatures made by the signing keys 
corresponding to the used transactions.
If these were predictable, our adversary could spend arbitrary transactions in 
the blockchain --- which is designed to be hard.
Thus Alice can predict \(t_s\) with negligible probability, \ie \(t_s\) must 
have been published on the blockchain before being included in her proof share.

According to \cref{TemporallyRelated}, we must also prove that a proof share has 
not been created after a certain time.
Otherwise Grace can argue that the proof share was created after the protest.
The hash values of the proof shares are committed to the blockchain, thus there 
is a negligible probability that they were created after that.
Alice would have to choose a value \(y\) in the domain of the hash function 
\(\Hash\) and then find a preimage \(x\) such that \(y = \Hash[x]\) and \(x\) is 
a valid proof.
If \(\Hash\) is collision resistant, then finding \emph{any} preimage is hard.

\paragraph{Linkability}%
\label{analysis-linkability}

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that Alice can 
provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) and make the witness accept in the protocol
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
This is thus reduced to the security of the \(\AC\) scheme and how often Alice 
can get a valid signature on a secret key from the \ac{CA}.

\paragraph{Spatial eligibility}%
\label{analysis-spatial}

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed on the location when the proof share was created.
Thus we must ensure that Alice cannot forge undeserved witness signatures, which 
is ensured using the same linkability mechanism as above.
To forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l),
\end{multline*}
while not knowing a signature on the secret key \(\sk_W'\).
Thus she must break the \(\AC\) scheme to succeed or get a valid signature on 
\(\sk_W'\) from the \ac{CA}.
(Note that Alice can produce one witness signature for herself, since she has 
access to her own \(\sk_P\), but no more.)

\paragraph{Designated protest}%
\label{analysis-designated}

\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
share) for another event --- or someone else using her proof-share for another 
event.
This is prevented with the use of \(\cid\) in the proof shares.
Thus to reuse the proof share for another protest, with a different manifesto, 
one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
  \Hash[\mfst']\).

There is also another case of collision that we must prevent.
Consider that Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause 
identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), 
with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice would construct a manifesto \(m\) such that \(\Hash[m] = \pid\), 
then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the 
protest with manifesto \(m\).
This means that we must separate the mechanisms used for participating and 
witnessing.
The protocol achieves this by the fact that \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
\]
does not include \(\cid\) whereas \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\]
does.
Thus the verification process differs for the two types of proofs.
(An alternative approach would have been to compute them differently, \eg 
\(\pid = \AC[PRF]_{\sk}(x) = g_T^{1/(\sk+x)}\) but \(\wid = 
  g_T^{1/(\sk+x+1)}\).)

@@

We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable 
across protests (but linkable within one protest due to \cref{CountOnce}).
It follows from the properties of \(\ACprf\) that \(\pid = 
  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are 
unlinkable if \(\cid\neq \cid'\).

Now to \cref{ProofUnlink}.
Given \(\pid\), Grace cannot distinguish whether \(\pid = 
  \ACprf[_{\sk_A}][\cid]\), \(\pid = \ACprf[_{\sk_A}][\cid']\) or \(\pid = 
  \ACprf[_{\sk_B}][\cid]\) due to the properties of \(\AC\).

However, say that a witness works for Grace.
This witness interacts with Alice directly, \ie has (physically) identified her.
The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) 
and to verify the \ac{PPK}.
\daniel{This assumes that I will do the changes to hide \(\cid\) from the 
  witness in the \ac{PPK}.}
Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
share.
The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
\daniel{Fix this.}
Now Grace can link \(\cid\) (and thus the opinions in the manifesto) to Alice.

>>>>

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify that their participation proofs (\ie proof shares) are indeed included in the count computed.
As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, \pi_{\wid}\)) are committed to the blockchain and available from a public and permanent storage (see \cref{fig:ProtocolOverview}).
Thus, Alice and Bob can simply check that all of their proof shares are indeed there and the security of individual verifiability depends on the properties of the blockchain and storage.

\Cref{UniversalVerif} requires also that anyone can check the result and that all participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can download them, verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid}\)) the proofs and count them.
As for individual verifiability, the security of universal verifiability is reduced to the properties of the blockchain and storage but also the eligibility verification, which we will discuss next.

\subsection{Eligibility verifiability}
\label{analysis-eligibility}

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \PRIVO, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
We will now analyze these properties.

\paragraph{Temporal eligibility}
\label{analysis-temporal}

\Cref{TemporallyRelated} ensures freshness, as Alice cannot simply resubmit an old proof as a new one.
In general, freshness requires the prover to respond to an unpredictable challenge.
The challenge here is to include the hash value at the head of the blockchain at the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof share).
As it is the case in the construction of blockchains, the hash value at the head depends on the previous blocks in the chain.
Thus, the predictability of \(t_s\) depends on the predictability of the blocks, which depends on the predictability of the transactions and the nonce needed by the miner.
In turn, the transactions depend on the signatures made by the signing keys corresponding to the used transactions.
If these were predictable, the adversary could conduct arbitrary transactions in the blockchain --- which is assumed to be hard by design.
Thus, Alice can predict \(t_s\) only with negligible probability, as \(t_s\) must have been published on the blockchain before being included in her proof share.

According to \cref{TemporallyRelated}, we must also prove that a proof share has not been created after a certain time.
Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
The hash values of the proof shares are committed to the blockchain, which means that there is a negligible probability that they were created after that.
Alice would have to choose a value \(y\) in the domain of the hash function \(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) is a valid proof.
If \(\Hash\) is collision resistant, finding \emph{any} preimage is hard.

\paragraph{Linkability}
\label{analysis-linkability}

\Cref{CountOnce} is required to prevent Sybil attacks, in the sense that Alice cannot provide two participation proofs for specific protest and thus be counted twice.
This possibility is prevented by the use of \(\pid\).
Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key \(\sk_P'\) and make the witness accept in the protocol
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
As a consequence, this is reduced to the security of the \(\AC\) scheme and how often Alice can get a valid signature on a secret key from the \ac{CA}.

\paragraph{Spatial eligibility}
\label{analysis-spatial}

\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed on the location when the proof share was created.
To realize this, we have to ensure that Alice cannot forge witness signatures, which is realized by using the same linkability mechanism as above.
To forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l),
\end{multline*}
while not knowing a signature on the secret key \(\sk_W'\).
Thus, she must break the \(\AC\) scheme to succeed or get a valid signature on \(\sk_W'\) from the \ac{CA}.
The latter could be done if she can find people willing to collude.
However, due to the assumptions done in \cref{ProtocolVerification}, we either assume that we can trust (dedicated) witnesses or that Alice cannot collude with more than a threshold \(\theta\) of witnesses (of course this two approach could be combine).
Remark that Alice can produce one witness signature for herself, since she has access to her own \(\sk_P\), but no more.

\paragraph{Designated protest}
\label{analysis-designated}

\Cref{DesignatedEvent} is to prevent Alice (or someone else) from reusing the same proof (or proof share) for another event.
This possibility is prevented through the use of \(\cid\) in the proof shares.
To reuse the proof share for another protest, with a different manifesto, one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = \Hash[\mfst']\).

There exists another case of collision that we must prevent.
Consider the situation in which Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice construct a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
This means that we must separate the mechanisms used for participating and witnessing.
The protocol achieves this by the fact that \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
\]
does not include \(\cid\) whereas \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\]
does.
Thus, the verification process differs for the two types of proofs.
(An alternative approach would have been to compute them differently, for instance \(\pid = \AC[PRF]_{\sk}(x) = g_T^{1/(\sk+x)}\) but \(\wid = g_T^{1/(\sk+x+1)}\).)

@@

We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable across protests but linkable within one protest due to \cref{CountOnce}.
It follows from the properties of \(\ACprf\) that \(\pid =  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are unlinkable if \(\cid\neq \cid'\).

Afterwards to get the property \cref{ProofUnlink}.
Given \(\pid\), Grace cannot distinguish whether \(\pid = \ACprf[_{\sk_A}][\cid]\), \(\pid = \ACprf[_{\sk_A}][\cid']\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the properties of \(\AC\).

However, consider the situation in which the witness works for Grace.
This witness interacts with Alice directly and might have (physically) identified her.
The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) and to verify the \ac{PPK}.
\daniel{This assumes that I will do the changes to hide \(\cid\) from the witness in the \ac{PPK}.}
Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
share.
The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
\daniel{Fix this.}
If this occurs, Grace could link \(\cid\) (and thus the opinions in the manifesto) to Alice.

### 2018-08-14 paper/intro.tex

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they also lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

@@

\emph{Contributions.} In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
%Seb: once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.

\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
Finally, we conclude with a discussion and future works in \cref{Conclusion}.

>>>>

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{RelatedWork}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

@@

\emph{Contributions.} In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{DistanceBounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
}
\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
Finally, we conclude with a discussion \cref{Discussion} and future work in \cref{Conclusion}.

### 2018-08-14 paper/properties.tex

To go back to the scenario stated in the introduction in our setting, we have two potential adversaries: Alice and Grace.
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Grace, the totalitarian dictator, is to decrease the count but also additionally to re-identify some of the participants in order to arrest them or forcefully convince them to change their minds.
In the following two subsections, we will define the desired security properties.

@@

In addition to the verification requirements, we also need to define the privacy properties.
In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
\item[Vote privacy:] the voting does not reveal any individual vote.
\item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
\end{description}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.
Coercion resistance is probably not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.

>>>>

To go back to the scenario stated in the introduction, we have two potential adversaries: Alice and Grace.
Alice is a participant of the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Grace, the government Alice protests against, is to not only decrease the count, but also to re-identify some of the participants in order to arrest them or forcefully convince them to change their minds.
In the following two subsections, we will define the desired security properties.

@@

In addition to the verification requirements, we also need to define the privacy properties.
In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
\item[Vote privacy:] the voting does not reveal any individual vote.
\item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
\end{description}
\sonja{discussion about applicable properties here, more sources and alternative properties}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.
Coercion resistance is probably not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
